ToDo:
machine locations
machine number
machine role

optimize queries

DB link error --> account for any issues

IF SF goes down, what do we do

SF: Write:#75 Read: #5
TO: Write: #8.3 Read: #5

LN: Write: #8.3 Read: #45
IN: Write: #8.3 Read: #45

# = percent

Machines can be hosted at any of the locations where there is an office now. 
They are willing to add an additional hosting location in anther location if it makes sense. 
Your design needs to discuss:
- where are machines located and how many are they and what role do they play.

- how do applications need to be written/configured to guarantee that the reports 
are generated from data located in the same place as the person requesting the report.

- if there is a network failure connecting London or Tokyo, 
how do they continuing being able to do reports and what are the implications.

- if there is network failure that isolates San Francisco, 
what happens to the ability to update date and run reports?

- what happens if one node fails someplace in the environment? 
How many nodes can fail before the whole system becomes non-functional?

Design:

So basically we have 4 areas. SanFran, Tokyo, London, and Indy

SF | TO | LN | IN
SF - 3 (pri)
TO - arbiter
LN - 2 || 3 (sec)
IN - 2 || 3 (sec)

Currently we are looking at 8 machines.
3 in SF so that if one goes down we can perform an election and keep it running as best we can
arb in TO because if we are left with 1 machine, we can still get a majority no matter what
2 or 3 in LN and IN depending on input. The reason we could try 2 is because they are predominately RO
but for the sake of safety, we could try 3, still get elections and majority, then could be R/W if need be

Total Machines: 10 depending.

If we configure it in this sense,

Say A,B,C are SF
Say D,E,F are LN
Say G,H,I are IN
Say J is arb in TO

Pri in SF,
LN,IN,TO down no worries

SF goes down, TO arbites to determine if possible election needed
LN,IN have 3 availble, will call for an election, get majority, have an election,
cluster stays Read/Write, we gucci

Under this design, LN goes down, IN steps up. TO goes down, its an arb, no worries

Under this design, we could have 1 node disappear from each station.
i.e SF,IN,LN drop down to 2 nodes, with an Arb, we still have Odd, so elections could be made
and we could still be in business. should 2 nodes fail in each,
each SF,IN,LN drop to 1 with 1 arb, if SF remains running as Pri with 1 node we still have R/W
and if anything drops below that, we have 2 nodes with 1 arb, still allowing an election if necessary.

Under this design, we could lose 6 nodes and still be alright, but without an arbiter,
we could lose 3.

